Topological Approach to Finding Blackholes in Directed Networks

### 2019-12-08 blackholes/pavt/article.tex
Typos

\begin{definition}
Subset of nodes $B \in V$ is called a blackhole if  the following two conditions are satisfied: 
1) Subgraph $G'(B, E')$ induced by $B$ is weakly connected, 
%$|B| \geq 2$,
and
2) there is no such pair of nodes $(u,v)$ that $u \in B$, $v \in V \backslash B$ and $(u,v) \in E$.
\end{definition}

@@

\begin{definition}
For a given directed graph $G(V,E)$ if $v \in V$ is reachable from $u \in V$, then we say $u$ is a predecessor of $v$ and $v$ is a successor if $u$.
If there is an edge from $u$ to $v$, then $u$ is a direct predecessor of $v$, and $v$ is a direct successor if $u$.
\end{definition}

@@

\subsection{Known Issues}
In this section we discuss applicability of the iBlackhole algorithm, proposed in \cite{li2010detecting}.
The iBlackhole algorithm (see Algorithm \ref{alg:iblackhole}) is designed for searching blackholes of fixed size. Potentially it has a great resource of parallelism, however this work does not cover the case of large scale graphs, as they only run their algorithm on 1500 node networks, which are quite
a small size.

@@

\begin{definition}
	Given graph $G(V, E)$, a root $r \in Roots(G)$, $topSortOrder_r$ -- topological sort of $Closure(r)$ and 
	$|Closure(v)|,\ \forall v \in Closure(r)$ --
	closure sizes of all nodes reachable from $r$. We say that node $v$ is special under root $r$, if its closure size  equals to its 1-based index in array $topSortOrder_r$. Note that set of special nodes $Special_r \subseteq Closure(r)$.
\end{definition}

\begin{remark}
    Specialness of a node is decided independently under different roots. One node can be special for root $r1$ and non-special for $r2$ at
    the same time. It is illustrated in Figure \ref{fig:specialnodes}.
\end{remark}

@@

\FIXME{посмотреть еще раз внимательно}
\begin{proof}
    By definition of special node $v$ has closure size equal to its index in $topSortOrder_r$. All the nodes of $Closure(v)$ has lesser indices 
    in $topSortOrder_r$ than $v$. Hence $\forall $u$ \in Closure(v)$ $u$ is reachable from $v$.
\end{proof}

>>>>

\begin{definition}
Subset of nodes $B \subseteq V$ is called a blackhole if  the following two conditions are satisfied: 
1) Subgraph $G'(B, E')$ induced by $B$ is weakly connected, 
%$|B| \geq 2$,
and
2) there is no such pair of nodes $(u,v)$ that $u \in B$, $v \in V \backslash B$ and $(u,v) \in E$.
\end{definition}

@@

\begin{definition}
For a given directed graph $G(V,E)$ if $v \in V$ is reachable from $u \in V$, then we say $u$ is a predecessor of $v$ and $v$ is a successor if $u$.
If there is an edge from $u$ to $v$, then $u$ is a direct predecessor of $v$, and $v$ is a direct successor of $u$.
\end{definition}

@@

\subsection{Known Issues}
In this section we discuss applicability of the iBlackhole algorithm, proposed in \cite{li2010detecting}.
The iBlackhole algorithm (see Algorithm \ref{alg:iblackhole}) is designed for searching blackholes of fixed size. Potentially it has a great resource of parallelism, however this work does not cover the case of large scale graphs, as they only run their algorithm on 1500 node networks, which is quite
a small size.

@@

\begin{definition}
	Given graph $G(V, E)$, a root $r \in Roots(G)$, $topSortOrder_r$ -- topological sort of $Closure(r)$ and 
	$|Closure(v)|\ \forall v \in Closure(r)$ --
	closure sizes of all nodes reachable from $r$. We say that node $v$ is special under root $r$, if its closure size  equals to its 1-based index in array $topSortOrder_r$. Note that set of special nodes $Special_r \subseteq Closure(r)$.
\end{definition}

\begin{remark}
    Specialness of a node is decided independently under different roots. One node can be special for root $r_1$ and non-special for $r_2$ at
    the same time. It is illustrated in Figure \ref{fig:specialnodes}.
\end{remark}

@@

\FIXME{посмотреть еще раз внимательно}
\begin{proof}
    By definition of special node $v$ has closure size equal to its index in $topSortOrder_r$. All the nodes of $Closure(v)$ has lesser indices 
    in $topSortOrder_r$ than $v$. Hence $\forall u \in Closure(v)$ $u$ is reachable from $v$.
\end{proof}
